Extending the WebID Protocol with Access Delegation

### 2012-07-27 paper.tex
some small fixes in the introduction

Agents on the web communicate with each other through a limited number of actions: by making requests for resources (GET), or by creating resources ( POST or PUT ), or even by deleting resources...
Creation or deletion of resources usually require authentication of the agent making the request, and so in many cases do requests for information (GET).

@@

A \textit{WebID} is a URI that refers to an Agent - Person, Robot, Group or other thing that can have Intentions.
The WebID should be a URI which when dereferenced returns a representation whose description uniquely identifies the Agent as the controller of a public key~\cite{sporny-m-2011--a}.

The WebID protocol is used currently mostly for client authentication%
\footnote{Server authentication using IETF DANE follows much the same logic, except that the lookup for the identity is not done using the HTTP protocol but DNSSEC.}.
It is worth noting that the server serving the WebID profiles controls the identity of every agent whose URI is within that server's namespace.
This service is known as the Origin Server~\cite{barth-a-2011--a}.
It is the Origin of all resources served by it.

We can easily think of the Origin Server as not only able to respond to requests, but also as an agent able to make requests.
Indeed WebID authentication requires the server to make WebID Profile requests to other servers in order to verify the identity of agents making a request to it.
The WebID spec describes this task as being accomplished by a separate agent, the WebID Verifier - which could indeed be done by another service on the web (WebID Proxy Authentication servers).
But it can also be so closely tied to the web service that it would be natural to think of it as part of that same service.
The WebID Profile furthermore could be served by the same agent as the one making the request, in which case we have a minimal case of a peer to peer communication.
Note that fetching a WebID profile for WebID Authentication should be done anonymously, for fear of authentication deadlocks.

>>>>

Agents on the web communicate with each other through a limited number of actions: by making requests for resources (GET), by creating resources (POST or PUT), or even by deleting resources \ldots
Creation or deletion of resources usually require authentication of the agent making the request, and so in many cases do requests for information (GET).

@@

A \textit{WebID} is a URI that refers to an agent - person, robot, group or other thing that can have intentions.
The WebID should be a URI which when dereferenced returns a representation whose description uniquely identifies the agent as the controller of a public key~\cite{sporny-m-2011--a}.

The WebID protocol is used currently mostly for client authentication%
\footnote{Server authentication using IETF DANE follows much the same logic, except that the lookup for the identity is not done using the HTTP protocol but DNSSEC.}.
It is worth noting that the host serving the WebID profiles controls the identity of every agent whose URI is within that server's namespace.
This service is known as the origin server~\cite{barth-a-2011--a}.
It is the origin of all resources served by it.

We can easily think of the origin server as not only able to respond to requests, but also as an agent able to make requests.
Indeed WebID authentication requires the server to make WebID profile requests to other servers in order to verify the identity of agents making a request to it.
The WebID spec describes this task as being accomplished by a separate agent, the WebID verifier - which could indeed be done by another service on the web (WebID proxy authentication servers).
But it can also be so closely tied to the web service that it would be natural to think of it as part of that same service.
The WebID profile furthermore could be served by the same agent as the one making the request, in which case we have a minimal case of a peer to peer communication.
Note that fetching a WebID profile for WebID authentication should be done anonymously, for fear of authentication deadlocks.\todo{ST: why that? done -> allowed}
